---
title: 'RAF Technical Note: Processing Algorithms'
author: "Author: NCAR Research Aviation Facility Science and Instrumentation Group"
date: "Date: June, 2022"
output:
  bookdown::gitbook:
    config:
      toc:
        collapse: section
      fontsettings:
        theme: white
        family: sans
        size: 2
      download: true
    lib_dir: assets
    toc_depth: 2
    keep_tex: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
  html_document:
    df_print: paged
    keep_tex: yes
    split_by: chapter+number
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::pdf_book:
    lib_dir: assets
    toc_depth: 2
    keep_tex: yes
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 2
  bookdown::word_document2:
    toc: true
    toc_depth: 2
  bookdown::html_book:
    lib_dir: assets
    split_by: chapter+number
    keep_tex: yes
    toc: yes
    toc_depth: 2
    toc_float: true
  bookdown::html_document2:
    keep_tex: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
    config:
      toolbar:
        position: static
documentclass: book
site: bookdown::bookdown_site
always_allow_html: yes
---

```{r init, include=FALSE}
options(tinytex.verbose = TRUE)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
library(magrittr)
```

# Preface {-#index}

This site serves as the RAF Technical Note on processing algorithms that are used for processing data collected on the RAF research aircraft. The variables that appear in archived data are defined here, and the algorithms used in their calculation are described. This document does not describe the instrumentation used, but there are many links to such descriptions. The goal of this document is to describe both current and past algorithms, so it is expected that this document will be modified often so that it can remain current.
```{r include = TRUE, echo = FALSE}
## construct data.frame for the following table:
CHANGELOG <- data.frame("Revision" = c('June, 2022 (Draft)', 'June, 2019', 'February, 2019'))
CHANGELOG$GitHub_Tag <- c('Release V2022.0', 'Release V2019.1', 'Release V2019.0')
CHANGELOG$Summary <- c('Updates to constants based on CODATA published values (2018) (SB). Numerous updates to 3. The State of the Aircraft and 4. The State of the Atmosphere (SB, CW). Link to manuscript on Total Air Temperature (TAT) data quality analysis below Eq. 4.14 (JC). Correction to Eq. 7.9 to have UPRESS multiplied by 10 (MR). Other cosmetic changes have been made to the PDF-format version of June 2019, which was generated using the program LyX (WC).', 'License has been changed from GPL to BSD-3.', 'Original release.')
```
## Document Change Log
```{r include = TRUE}
knitr::kable(CHANGELOG, align=c('cccl')) %>% kable_styling(bootstrap_options = 'bordered') %>%
  scroll_box(width='80%')
```
<p><br>Link to PDF of V2019.0: [ProcessingAlgorithms_022019.pdf](www/ProcessingAlgorithms_022019.pdf)</br></p>

## Citation Information
When referencing this RAF Technical Note on processing algorithms, please use the DOI 10.26023/zc3gpm25 - for example as a citation: UCAR/NCAR - Earth Observing Laboratory (2022) RAF Technical Note: Processing Algorithms. UCAR/NCAR - Earth Observing Laboratory. https://doi.org/10.26023/zc3gpm25 V2022.0 Retrieved enter date here.

```{r child='Children/boxStyles.Rmd'}

```

```{r child='Children/Section1.Rmd'}
```

```{r child='Children/Section2.Rmd'}
```

```{r child='Children/Section3.Rmd'}
```

```{r child='Children/Section4.Rmd'}
```

```{r child='Children/Section5.Rmd'}
```

```{r child='Children/Section6.Rmd'}
```

```{r child='Children/Section7.Rmd'}
```

```{r child='Children/Section8.Rmd'}
```

```{r child='Children/Section9.Rmd'}
```

```{r child='Children/Section10.Rmd'}
```

```{r child='Children/Appendices.Rmd'}
```
 
 ```{r child='Children/Index.Rmd'}
 ```

